### 2015-10-16 branches/kevin-1407/targetDP/doc/execution_model.tex
1407 feature branch
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@2755 40876441-3496-0410-a613-a2fca35b2ae2

The terminology ``host'' is used to refer to the CPU that is hosting
the execution of the application, and ``target'' to refer to the
device targeted for execution of data parallel operations. The target
can be the same CPU as the host, or it can be a separate device such
as an accelerator.

@@

To ensure that the target function has completed, a
\verb+targetSynchronize+ statement should follow the code location
where target function is launched. When the initial thread encounters
this statement, it will wait until the target region has completed. It
is possible for the initial thread to execute other instructions
(which do not depend on the results of the target function), after the
function launch but before the syncronisation call. This may result in
overlapping of host and target execution, and hence optimisation, in
some implementations. Once the target function has completed, the
initial thread will continue sequentially until another target
function launch is encountered.

@@

>>>>

The terminology ``host'' is used to refer to the CPU that is hosting
the execution of the application, and ``target'' to refer to the
device targeted for execution of data parallel operations. The target
could be the same CPU as the host, or it could be a separate device such
as an accelerator (depending on the hardware available).

@@

To ensure that the target function has completed, a
\verb+targetSynchronize+ statement should follow the code location
where target function is launched. When the initial thread encounters
this statement, it will wait until the target region has completed. It
is possible for the initial thread to execute other instructions
(which do not depend on the results of the target function), after the
function launch but before the synchronisation call. This may result in
overlapping of host and target execution, and hence optimisation, in
some implementations. Once the target function has completed, the
initial thread will continue sequentially until another target
function launch is encountered.

@@

\begin{comment}
Some text on reductions needed.
\end{comment}
